---
title: "Terror Types Manuscript II"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Dropbox/TAMU/Extra_Projects/Git_edits/Terror_types")

library(devtools)
library(stargazer)
library(tidyr)
library(dplyr)
```

## Regression Tables

This document displays the results of two analyses. First, two models that test what factors drive the reported **Concern** attribute. These are OLS regression models with the **Likelihood** and **Costs** attributes as the main predictors. Full discussion of this analysis is detailed in the manuscript appendix.

```{r data insert, echo = F }
# load data
Data_type2 <- read.csv("~/Dropbox/TAMU/Extra_Projects/Git_edits/Terror_types/Data/TerrorTypes_EditNov19.csv", 
                       header=TRUE, sep = ",", strip.white = T, na.strings = "")

# Rescale policy items (0-1 scale)
Data_type2$newforce <- ((Data_type2$Pol_force - 1)/3)
Data_type2$newscreen <- ((Data_type2$Pol_screenUS - 1)/4)
Data_type2$surv <- ((Data_type2$Pol_survMusl - 1)/3)
Data_type2$phone <- ((Data_type2$Pol_trackPh - 1)/4)

# Rescale attributes (0-1 scale)
Data_type2$conc_bomb <- ((Data_type2$concern_bomb - 1)/3)
Data_type2$conc_cyber <- ((Data_type2$concern_cyber - 1)/3)

Data_type2$like_bomb <- ((Data_type2$likely_bomb - 1)/3)
Data_type2$like_cyber <- ((Data_type2$likely_cyber - 1)/3)

Data_type2$ca_bomb <- ((Data_type2$cas_bomb - 1)/4)
Data_type2$ca_cyber <- ((Data_type2$cas_cyber - 1)/4)

## Add knowledge Index (based on media items)
Data_type2$media_index <- Data_type2$inform_papers + Data_type2$inform_Fox + Data_type2$inform_CNN + Data_type2$inform_MSNBC +
  Data_type2$inform_network + Data_type2$inform_online + Data_type2$inform_radio + Data_type2$inform_social

#change variables names
names(Data_type2)[names(Data_type2)=="KnowGen"] <- "Knowledge"
names(Data_type2)[names(Data_type2)=="DOV_XPARTY7"] <- "Party"
names(Data_type2)[names(Data_type2)=="PPAGE"] <- "Age"
names(Data_type2)[names(Data_type2)=="PPGENDER"] <- "Gender"

```


```{r results = 'asis', message=F, echo=FALSE }

m.concern1 <- lm(conc_bomb ~ like_bomb + ca_bomb + media_index + Party + Age + PPEDUCAT +
                    Gender + PPINCIMP, data = Data_type2)

m.concern2 <- lm(conc_cyber ~ like_cyber + ca_cyber  + media_index + Party + Age + PPEDUCAT +
                    Gender + PPINCIMP, data = Data_type2)

# Regression table 
stargazer(m.concern1, m.concern2, type = "latex", header = FALSE, 
          style = "ajps", title = "Drivers of Concern Attribute", 
          dep.var.labels = c("Concern:Conventional", "Concern:Cyber"),
          covariate.labels = c("Likelihood:Conventional", "Costs:Conventional", "Likelihood:Cyber", "Costs:Cyber",
                               "Media Index", "Partisanship", "Age", "Education", "Gender", "Income"),
          omit.stat = c("LL","ser","f"), no.space = TRUE) #Latex table

```

\break

The second analysis assess the effects of the primary **Likelihood** and **Costs** attributes on two policy options: offensive (military intervention) and defensive (airport security). These are two OLS regression models with the **Likelihood** and **Costs** attributes (by method of attack) as the central predictors. In the main text, the results are displayed using a combined coeficient plots.

```{r results = 'asis', message=F, echo=FALSE}
m.force1 <- lm(newforce ~ like_bomb + ca_bomb + like_cyber + ca_cyber + media_index + Party + Age + PPEDUCAT +
                         Gender + PPINCIMP, data = Data_type2)

m.screen1 <- lm(newscreen ~ like_bomb + ca_bomb + like_cyber + ca_cyber + media_index + Party + Age + PPEDUCAT +
                          Gender + PPINCIMP, data = Data_type2)

# Regression table 
stargazer(m.force1, m.screen1, type = "latex", header = FALSE, 
          style = "ajps", title = "Counterterrorism Policy Support", 
          dep.var.labels = c("Offensive (Military Force)", "Defensive (Airport Security)"),
          covariate.labels = c("Likelihood:Conventional", "Costs:Conventional", "Likelihood:Cyber", "Costs:Cyber",
                               "Media Index", "Partisanship", "Age", "Education", "Gender", "Income"),
          omit.stat = c("LL","ser","f"), no.space = TRUE) 

```

